---
title: "Everybody"
author: "Kandis Combs!"
date: "11/19/19"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
avast <-read.csv(file="avastivironal.csv",header=TRUE)
avastf <- filter(avast,sex=="gal")
avastb <-filter(avast,sex=="guy")
avastG <-filter(avast,LGBTQ=="gay")
avastd <-filter(avast,DrugUser=="yes")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aides (abacavirinol) is under test in clinical trials. I will analyze the effectiveness of this drug across the board using different sex and gender. I will Consider population subgroups by gender, drug use, and sexual orientation.The data was imported from the abacavironal file and broken up into 5 different sections. 

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

I will use barcharts, tables and chisq.test to analyysis the data. I have 5 different sections to anlayze together and individually. 

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~infected + treatment,data=avast,type="percent")
```
This barchart shows that 40% of the people that used this drug still got aids and 59 % that got the placebo got aids. It looks as if the drug is working for the girls.


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
table1 <- xtabs(~infected + treatment, data=avast)
rowPerc(table1)
colPerc(table1)
```
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
Because the p value is 2.333e-o7. I fail to reject the null hypothesis

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!--> There is a relationship betwwen taking the drug and not taking the drug and getting aid. 40% of the gals that took the drug still got aides but almost 60 % of the gals that didnt get the drug but took the placebo got aids and almost the exact same amount that didnt get aids took neither the drug or placebo.
